\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-18 paper/main.tex
.

\abstract{\textbf{Motivation:} \textit{In silico} drug--target
  interaction (DTI) prediction is crucial for drug discovery and
  down-stream tasks, such as drug indication and drug--disease
  prediction. However, DTI datasets are prone to certain biases,
  skewing the effective predictive expressiveness over those
  datasets. Additionally, only few approaches combine phenotypical and
  molecular features for DTI prediction. \\
  \textbf{Results:} We present \name{} to combine molecular features
  and functional information with protein--protein interaction
  networks under usage of graph convolutional neural networks, showing
  that phenotypic information localizes on the interaction network. We
  hereby focus on protein-centric evaluation, predicting drugs that
  may target specific targets. We further show that common
  drug--target interaction datasets contain intrinsic biases, majorly
  affecting predictive performance of compared models. Additionally,
  we propose an modified evaluation scheme and metric to circumvent
  such skews and to better reflect the problem DTI prediction methods
  aim to solve. \\
  \textbf{Availability:} Source code and data used in \name{} are
  available at \url{https://github.com/THinnerichs/DTI-VOODOO} \\
  \textbf{Contact:}
  \href{tilman.hinnerichs@kaust.edu.sa}{tilman.hinnerichs@kaust.edu.sa}
  \\
  \textbf{Supplementary information:}Supplementary data are
  available at \textit{Bioinformatics} online.}

>>>>

\abstract{\textbf{Motivation:} \textit{In silico} drug--target
  interaction (DTI) prediction is important for drug discovery and
  drug repurposing.  Approaches to predict DTIs can proceed
  indirectly, top-down, using phenotypic effects of drugs to identify
  potential drug targets, or they can be direct, bottom-up and use
  molecular information to directly predict binding potentials.
  Both approaches can be combined with information about interaction
  networks,

  However, DTI datasets are prone to certain biases,
  skewing the effective predictive expressiveness over those
  datasets.
  \textbf{Results:} We present \name{} to combine molecular features
  and functional information with protein--protein interaction
  networks under usage of graph convolutional neural networks, showing
  that phenotypic information localizes on the interaction network. We
  hereby focus on protein-centric evaluation, predicting drugs that
  may target specific targets. We further show that common
  drug--target interaction datasets contain intrinsic biases, majorly
  affecting predictive performance of compared models. Additionally,
  we propose an modified evaluation scheme and metric to circumvent
  such skews and to better reflect the problem DTI prediction methods
  aim to solve. \\
  \textbf{Availability:} Source code and data used in \name{} are
  available at \url{https://github.com/THinnerichs/DTI-VOODOO} \\
  \textbf{Contact:}
  \href{tilman.hinnerichs@kaust.edu.sa}{tilman.hinnerichs@kaust.edu.sa}
  \\
  \textbf{Supplementary information:}Supplementary data are
  available at \textit{Bioinformatics} online.}
